Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training

### 2024-11-29 manuscript/manuscript.Rmd
updated manuscript

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
wordcount         : "6703"
bibliography      : ["references.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
note              : "\\clearpage" ## this moves the author note section to a second page
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

Importantly, given that we were interested in the mechanisms that underlie training vs. no-training, as well as comparisons between different types of training (linguistic vs. action vs. both), only the post-training session was necessary to capture and quantify these effects. Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state [@weisberg2007]. All other aspects of the pre-registration were unchanged. In addition, all of the analysis code used in this paper have been made available on the open science framework ([https://osf.io/ea6gk/](https://osf.io/ea6gk/). Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly. Therefore, the raw data are only available from the authors upon request. Since the current manuscript was written in R using the papaja() package [@R-papaja], it is also computationally reproducible and available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).

>>>>

  <!-- https://tinyurl.com/ybremelq -->
keywords          : "evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity"
wordcount         : "6698"
bibliography      : ["references.bib", "r-references.bib"]
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle"
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
note              : "\\clearpage" ## this moves the author note section to a second page
editor_options: 
  chunk_output_type: console
header-includes:
  - \raggedbottom
---

@@

Importantly, given that we were interested in the mechanisms that underlie training vs. no-training, as well as comparisons between different types of training (linguistic vs. action vs. both), only the post-training session was necessary to capture and quantify these effects. Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state [@weisberg2007]. All other aspects of the pre-registration were unchanged. In addition, the analysis code used in this paper is available online, and the manuscript was written in R using the papaja() package [@R-papaja], which means it is  computationally reproducible. The code and manuscript are available via GitHub ([https://github.com/rich-ramsey/knot_dmc](https://github.com/rich-ramsey/knot_dmc)).  Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly. Therefore, the raw data are only available from the authors upon request.

### 2024-11-29 manuscript/manuscript.tex
updated manuscript

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6703}
\usepackage{lineno}

@@

Importantly, given that we were interested in the mechanisms that underlie training vs.~no-training, as well as comparisons between different types of training (linguistic vs.~action vs.~both), only the post-training session was necessary to capture and quantify these effects. Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state (Weisberg et al., 2007). All other aspects of the pre-registration were unchanged. In addition, all of the analysis code used in this paper have been made available on the open science framework (\url{https://osf.io/ea6gk/}. Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly. Therefore, the raw data are only available from the authors upon request. Since the current manuscript was written in R using the papaja() package (Aust \& Barth, 2023), it is also computationally reproducible and available via GitHub (\url{https://github.com/rich-ramsey/knot_dmc}).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{evidence accumulation modelling, training, learning, action, naming, cognitive mechanisms, plasticity\newline\indent Word count: 6698}
\usepackage{lineno}

@@

Importantly, given that we were interested in the mechanisms that underlie training vs.~no-training, as well as comparisons between different types of training (linguistic vs.~action vs.~both), only the post-training session was necessary to capture and quantify these effects. Indeed, Cross and colleagues (2012), in their original study, included only results from the post-training session in their final analysis, as this session is thought to be more consistent and reflect the participants' learned state (Weisberg et al., 2007). All other aspects of the pre-registration were unchanged. In addition, the analysis code used in this paper is available online, and the manuscript was written in R using the papaja() package (Aust \& Barth, 2023), which means it is computationally reproducible. The code and manuscript are available via GitHub (\url{https://github.com/rich-ramsey/knot_dmc}). Given that the data were collected several years before 2012, it was not yet routine to request explicit consent to share data publicly. Therefore, the raw data are only available from the authors upon request.
